### 2014-08-23 doc/tacs2014/article.tex
README basics, added TACS article early draft

% Document title
% ==============
% Draft for conference/workshop paper to be submitted to http://tappcs.blogspot.mx/
% 2--4 pages in Spanish or English.

\documentclass[10pt,conference,a4paper]{IEEEtran}
\usepackage{hyperref}
%\usepackage{

\title{Some Nice Title Goes Here, Eventually\ldots}

\author{
	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \texttt{fredrik.karlstrm@uabc.edu.mx}}
	\and
	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \texttt{your-cool-academic-email-here@uabc.edu.mx}}
}

%\markboth{TACS 2014 and more info here}{} % Only on journal papers, apparently...

\begin{document}
	\maketitle

	\begin{abstract}
		Oh golly, this is where the abstract should go.
		``I can hardly wait to begin writing it!''

		Or well, let's see how things turn out in the body first, eh.
	\end{abstract}
	\medskip
	\begin{IEEEkeywords}
		Intelligent character recognition, Japanese writing, \ldots
	\end{IEEEkeywords}

	\section{Problem description}

	Any form of digital handwriting recognition is a complex undertaking,
	where the performance of the system is impacted by a multitude of factors -- spanning
	everything from the quality and quantity of training data, to resilience toward input
	translation, rotation, and noise. As the number of candidate categories increases
	the size of the search space, however, the task quickly grows monumental.

	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
	as well as the sinographs commonly known as \emph{kanji} -- literally ``Han characters'' -- that stem from China.
	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list [ref] defines a set of 2,136
	baseline characters taught in elementary-- and secondary--school education. This set is far from exhaustive though:
	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji characters.

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	it becomes apparent that a monolithic system design would be both unwieldly and computationally expensive, depending on
	deep neural networks [ref?] for high performance.

	In this work, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each component. The design scheme also permits replacing classification strategies,
	and facilitates the parallelization of network training.

	\section{Previous work}

	Thus concludes this tale of Foo Bar, whose epic journey had a tremendous
	impact on the field of cryptography. Thank you, Foo, for your contributions.

	\section{Proposed solution}

	Some text here, followed by a diagram. Divide and conquer!

	%\begin{figure}
	%\centering
	%\includegraphics[width=2.5in]{myfigure}
	%\caption{Simulation Results}
	%\label{fig_sim}
	%\end{figure}

	\subsection{Stroke feature extraction}

	\subsection{Category clustering}

	\subsection{Feedforward routing network}

	\subsection{Convolutional character classification network}

	\section{Experiments}

	This will be a short section\ldots
	Describe the simple online feature extractor and following clustering scheme.

	\section{Conclusions}

	This work is cool, now give complimentary M.Sc. plx?
	They did it for Donald Knuth\ldots :(

	\section{References}

\end{document}

### 2014-08-25 doc/tacs2014/article.tex
Elaborated slightly on previous work, experiments, and future work. Added overview diagram and bibtex.

@@
 \documentclass[10pt,conference,a4paper]{IEEEtran}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
+\usepackage{graphicx}
+\bibliographystyle{IEEEtran}
 %\usepackage{
@@
 	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
-	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \texttt{fredrik.karlstrm@uabc.edu.mx}}
+	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:fredrik.karlstrm@uabc.edu.mx}{\texttt{fredrik.karlstrm@uabc.edu.mx}}}
 	\and
 	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
-	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \texttt{your-cool-academic-email-here@uabc.edu.mx}}
+	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:foo@bar.com}{\texttt{your-cool-academic-email-here@uabc.edu.mx}}}
 }
@@
 	\begin{abstract}
-		Oh golly, this is where the abstract should go.
-		``I can hardly wait to begin writing it!''
-
-		Or well, let's see how things turn out in the body first, eh.
+		Quick content summary.
+		Motivation. (From 'Robust': High accuracy has been attained, but speedup/size improvements still important for mobile and desktop.)
 	\end{abstract}
@@
 	as well as the sinographs commonly known as \emph{kanji} -- literally ``Han characters'' -- that stem from China.
-	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list [ref] defines a set of 2,136
-	baseline characters taught in elementary-- and secondary--school education. This set is far from exhaustive though:
-	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji characters.
+	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
+	baseline characters taught in elementary-- and secondary--school education. This set is far from exhaustive, though:
+	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.
 
 	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
-	it becomes apparent that a monolithic system design would be both unwieldly and computationally expensive, depending on
-	deep neural networks [ref?] for high performance.
+	it becomes apparent that a monolithic system design would be both unwieldly and computationally expensive, requiring
+	deep neural networks \cite{ciresan2012multi} to attain high recognition rates.
 
@@
 
-	Thus concludes this tale of Foo Bar, whose epic journey had a tremendous
-	impact on the field of cryptography. Thank you, Foo, for your contributions.
+	Testing a cite \cite{zhu2014robust}.
+
+	\ldots
+
+	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
+	hidden Markov models for the purpose of online kanji recognition. By identifying and classifying
+	substrokes, which in turn are employed as search keys in a character dictionary, this approach vastly
+	reduced the memory requirements for both their models and their dictionary.
+
+	``Online Handwritten Kanji Recognition Based on Inter-stroke Grammar'' uses the A-H0-9 classification scheme,
+	and discusses the hierarchical structure of kanji.
+
+	Should we mention alternative solutions, such as SVMs?
 
@@
 
-	%\begin{figure}
-	%\centering
-	%\includegraphics[width=2.5in]{myfigure}
-	%\caption{Simulation Results}
-	%\label{fig_sim}
-	%\end{figure}
+	\begin{figure}
+		\centering
+		\includegraphics[width=2.75in]{./fig/model-overview.eps}
+		\caption{Model overview. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
+		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
+		\label{fig_model_overview}
+	\end{figure}
 
-	\subsection{Stroke feature extraction}
+	\subsection{Feature extraction}
 
@@
 
+	\ldots
+
+	Whereas in \cite{nakai2001substroke} strokes were segmented into substrokes and classified in
+	25 dimensions, our initial feature extraction strategy provides a coarse full--stroke classification
+	in 8 dimensions. By discarding ``pen--up motions,'' we render the system more resilient to erroneous
+	stroke order, at the cost of increasing variability within each cluster.
+
 	\section{Conclusions}
@@
 
-	\section{References}
+	\section{Future work}
+
+	The experimental results documented in this paper are an initial attempt at applying the proposed methodology;
+	numerous variations remain to be explored. With regard to online recognition, the explored feature extraction
+	strategy could be enhanced to break strokes into substrokes, diffentiate between long and short strokes, and take
+	pen--up movements into account. This alteration would in turn allow clustering on up to 25 dimensions, rather than the current 8.
+
+	By substituting the current coarse classifier with an offline feature extraction strategy, the entire system could
+	be evaluated on offline handwriting recognition datasets, such as\ldots.
+
+	Clustering\ldots
+
+	Finally, at the cluster--specific CANN--level, there is ample opportunity to tweak the network topology as well as
+	to apply a variety of best practices \cite{simard2003best} in order to enhance the final, fine--grain recognition results.
+
+	%\section{References}
+	\bibliography{./references}
 

### 2014-08-29 doc/tacs2014/article.tex
Added stats table and clustering-references

@@
 \documentclass[10pt,conference,a4paper]{IEEEtran}
+\usepackage[utf8x]{inputenc}
 \usepackage[hidelinks]{hyperref}
 \usepackage{graphicx}
+\usepackage{pgfplots}
+\usepackage[T1]{fontenc}
 \bibliographystyle{IEEEtran}
-%\usepackage{
+
+% This enables the kanji in the table, but all typefaces turn uglier.
+% Also must be generated with xelatex
+%\usepackage{xeCJK}
+%\setCJKmainfont{cyberbit.ttf}
 
@@
 	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
-	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:foo@bar.com}{\texttt{your-cool-academic-email-here@uabc.edu.mx}}}
+	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:everardo.gutierrez@uabc.edu.mx}{\texttt{everardo.gutierrez@uabc.edu.mx}}}
+}
+
+\pgfplotsset{
+	compat = newest,
+	xlabel near ticks,
+	ylabel near ticks
 }
@@
 	\begin{IEEEkeywords}
-		Intelligent character recognition, Japanese writing, \ldots
+		Intelligent character recognition, artificial neural network, handwriting recognition, Japanese writing, \ldots
 	\end{IEEEkeywords}
@@
 	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
-	baseline characters taught in elementary-- and secondary--school education. This set is far from exhaustive, though:
+	baseline characters taught in elementary-- and secondary--school education. \cite{hadamitzky2012japanese} This set is far from exhaustive, though:
 	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.
@@
 
-	Should we mention alternative solutions, such as SVMs?
+	``A linear--time elastic matching algorithm for on--line recognition of handwritten Japanese characters'' (Nakagawa)
+	presents the LTM--algorithm, an alternative and attractive way of extracting feature points.
+
+	Should we mention alternative solutions, such as SVMs? Tomoe does quite a good job, for instance. Not sure if there
+	are academic evaluations/references, though.
 
@@
 
+	As is proven in \cite{drineas2004clustering}, this is an NP-hard problem even in the case of $k = 2$.
+
+	Centroid-based clustering
+	"Seeks to minimize the average squared distance between points in the same cluster"
+	goal is to choose k centers so as to minimize $\varphi$, the total squared distance between each point and its closest center.
+
 	\subsection{Feedforward routing network}
@@
 	stroke order, at the cost of increasing variability within each cluster.
+
+	\subsection{Clustering}
+
+	\ldots decided to consider the value given by the ``rule of thumb'' $k \approx \sqrt{n / 2}$ proposed in \cite{mardia2005multivariate}
+	as an upper limit to the number of clusters.
+
+	$$ k_{max} = \sqrt{6,396 / 2} \approx 57 $$
+
+	The clusters were generated using the k--means++ algorithm,
+	a variation of Lloyd's algorithm that seeks to improve the selection of the initial centroids. \cite{arthur2007k}
+
+Total strokes: 78785
+
+\begin{table}
+	\renewcommand{\arraystretch}{1.3}
+	\caption{Statistical overview of \ldots}
+	\label{tbl_stroke_analysis}
+	\centering
+	\begin{tabular}{ c | c c c c c l }
+		\hline
+		  & \bfseries \% & \small $\sum$ & $\mu$ & $\sigma$ & Highest count \\ 
+		\hline
+		\hline
+		\bfseries A & $33.20\%$ & $26,160$ & $4.09$ & $2.33$ & $15$ & \\%(蠶) \\
+		\bfseries B & $1.47\%$  & $1,159$  & $0.18$ & $0.40$ & $2$  & \\%(摑) \\
+		\bfseries C & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
+		\bfseries D & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
+		\bfseries E & $0.31\%$  & $245$    & $0.04$ & $0.19$ & $2$  & \\%(霪) \\
+		\bfseries F & $12.72\%$ & $10,018$ & $1.57$ & $1.36$ & $10$ & \\%(鏐) \\
+		\bfseries G & $29.98\%$ & $23,616$ & $3.69$ & $1.96$ & $13$ & \\%(鱸) \\
+		\bfseries H & $22.32\%$ & $17,587$ & $2.75$ & $1.61$ & $11$ & \\%(靆) \\
+		\hline
+		\hline
+	\end{tabular}
+\end{table}
+
+	% Statistical representation was close to perfect after the initial
+	% segment of some 3k kanji
+	\begin{tikzpicture}[font=\small]
+		\begin{axis}[
+			ybar,
+			bar width=20pt,
+			xlabel={Stroke feature classification},
+			ylabel={Frequency (\%)},
+			ymin=0,
+			ymax=40,
+			%ytick=\empty,
+			xtick=data,
+			axis x line=bottom,
+			axis y line=left,
+			enlarge x limits=0.2,
+			symbolic x coords={A, B, C, D, E, F, G, H},
+			xticklabel style={anchor=base, yshift=-\baselineskip},
+			nodes near coords={\pgfmathprintnumber\pgfplotspointmeta}
+		]
+			\addplot[fill=white] coordinates {
+				(A, 33.2)
+				(B, 1.5)
+				(C, 0)
+				(D, 0)
+				(E, 0.3)
+				(F, 12.7)
+				(G, 30.0)
+				(H, 22.3)
+			};
+		\end{axis}
+	\end{tikzpicture}
+
+	\subsection{Preliminary results}
+
+	Not done yet, but here we go.
 

### 2014-08-30 doc/tacs2014/article.tex
Introduction section, revised problem description, new model overview figure

@@
 	\and
-	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
+	\IEEEauthorblockN{Everardo Guti\'errez L\'opez}
 	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:everardo.gutierrez@uabc.edu.mx}{\texttt{everardo.gutierrez@uabc.edu.mx}}}
@@
 }
-
-%\markboth{TACS 2014 and more info here}{} % Only on journal papers, apparently...
 
@@
 
+	\section{Introduction}
+
+	%Although new technologies aimed at digitalizing every aspect of daily life are introduced and adopted at an ever--increasing pace,
+	%handwriting still remains an integral
+
+	Although a variety of efficient digital input methods have become all but second nature to recent generations, for the vast majority,
+	handwriting remains an integral activity in daily life.
+	The importance to further improve upon the state of the art in handwriting recognition is underlined not only by the continued prevalence of 
+	handwriting, but also by the need to digitalize archived material, the significant role of handwriting in the development of fine motor skills,
+	and a variety of other areas of application, such as signature verification. \cite{plamondon2000online}
+
+	As an area of research, handwriting recognition predates even the digital computer. In 1888, Elisha Gray was awarded a patent \cite{gray1888telautograph}
+	for the ``Telautograph,'' which is considered a precursor to the stylus and digitizer.
+	In \cite{dimond1957devices} (1957), T.L. Dimond summarized early character recognition efforts and introduced the Stylator, another input recognition device.
+
+	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms; notable successful techniques in
+	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty} \cite{tappert1990state}
+
 	\section{Problem description}
@@
 	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
-	baseline characters taught in elementary-- and secondary--school education. \cite{hadamitzky2012japanese} This set is far from exhaustive, though:
-	the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.
+	baseline characters taught in elementary-- and secondary--school education. \cite{hadamitzky2012japanese}
+	This set is far from exhaustive, though: the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.
 
 	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
-	it becomes apparent that a monolithic system design would be both unwieldly and computationally expensive, requiring
-	deep neural networks \cite{ciresan2012multi} to attain high recognition rates.
+	and that other characteristics must be taken into account, it becomes apparent that the same designs that
+	yields highly accurate results on the western alphabet will not perform satisfactory when applied to asian character recognition, \cite{tappert1990state}
+	unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}
 
 	In this work, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
-	thereby reducing the complexity of each component. The design scheme also permits replacing classification strategies,
+	thereby reducing the complexity of each undertaking. The design scheme also permits replacing classification strategies,
 	and facilitates the parallelization of network training.
@@
 
+	In \cite{yang2003accelerating}, clustering, offline recognition, first comparing input to centroid character,
+	therafter search within.
+
 	``Online Handwritten Kanji Recognition Based on Inter-stroke Grammar'' uses the A-H0-9 classification scheme,
@@
 
-	Should we mention alternative solutions, such as SVMs? Tomoe does quite a good job, for instance. Not sure if there
+	Should we mention alternative solutions, such as SVMs? Zinnia (w/ Tomoe) does quite a good job, for instance. Not sure if there
 	are academic evaluations/references, though.
@@
 
-	Some text here, followed by a diagram. Divide and conquer!
-
 	\begin{figure}
@@
 		\includegraphics[width=2.75in]{./fig/model-overview.eps}
-		\caption{Model overview. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
-		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
+		\caption{The model consists of four components: a feature extractor, a clustering strategy,
+			a router (coarse classifier), and a fine--grained classifier.}
 		\label{fig_model_overview}
@@
 
+	By structuring the search space into mutually exclusive clusters of similar categories,
+	we are able to construct a corresponding number of fine classifiers that need only distinguish
+	between the categories within its own cluster. The smaller search space directly translates into a
+	significant reduction of model complexity, which in turn implies both a decrease in training time
+	and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
+	between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
+	improved as new training data is made available.
+
 	\subsection{Feature extraction}
+
+	The input data is processed by an algorithm, generating a coarse, n--dimensional representation of its principal features.
+	The feature vector is used to select which cluster the input belongs to.
+
+	A higher feature vector dimensionality allows for the construction of more finely--tuned clusters, but may well increase
+	the likelihood of ``misrouting,'' resulting in a failed classification.
+	% Actually, if a character is not found within the specified CANN, it could be passed to a neighboring cluster of similar composition
+
+	The coarse classifier may work on either online or offline input, or potentially a union of them both.
+	Examples of feature extractors include the LTM algorithm, and gradient--based solutions, both outlined in \cite{tanaka1999hybrid}.
 
@@
 
-	\ldots
+	\begin{figure}
+		\centering
+		\includegraphics[width=2.75in]{./fig/experimental-implementation.eps}
+		\caption{Experimental implementation. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
+		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
+		\label{fig_experimental_implementation}
+	\end{figure}
 
-	Whereas in \cite{nakai2001substroke} strokes were segmented into substrokes and classified in
-	25 dimensions, our initial feature extraction strategy provides a coarse full--stroke classification
-	in 8 dimensions. By discarding ``pen--up motions,'' we render the system more resilient to erroneous
-	stroke order, at the cost of increasing variability within each cluster.
+	\subsection{Data sources}
 
-	\subsection{Clustering}
+	KanjiVG \ldots
 
-	\ldots decided to consider the value given by the ``rule of thumb'' $k \approx \sqrt{n / 2}$ proposed in \cite{mardia2005multivariate}
-	as an upper limit to the number of clusters.
+	\subsection{Feature extraction}
 
-	$$ k_{max} = \sqrt{6,396 / 2} \approx 57 $$
-
-	The clusters were generated using the k--means++ algorithm,
-	a variation of Lloyd's algorithm that seeks to improve the selection of the initial centroids. \cite{arthur2007k}
-
-Total strokes: 78785
+	Figure of A-H compass. Explanation.
 
@@
 		\renewcommand{\arraystretch}{1.3}
-	\caption{Statistical overview of \ldots}
+		\caption{Stroke type frequency distribution overview }
 		\label{tbl_stroke_analysis}
@@
 			\hline
+			            & $100.00\%$   & $78,785$ &        &        &      & \\
 			\hline
@@
 
-	% Statistical representation was close to perfect after the initial
-	% segment of some 3k kanji
-	\begin{tikzpicture}[font=\small]
-		\begin{axis}[
-			ybar,
-			bar width=20pt,
-			xlabel={Stroke feature classification},
-			ylabel={Frequency (\%)},
-			ymin=0,
-			ymax=40,
-			%ytick=\empty,
-			xtick=data,
-			axis x line=bottom,
-			axis y line=left,
-			enlarge x limits=0.2,
-			symbolic x coords={A, B, C, D, E, F, G, H},
-			xticklabel style={anchor=base, yshift=-\baselineskip},
-			nodes near coords={\pgfmathprintnumber\pgfplotspointmeta}
-		]
-			\addplot[fill=white] coordinates {
-				(A, 33.2)
-				(B, 1.5)
-				(C, 0)
-				(D, 0)
-				(E, 0.3)
-				(F, 12.7)
-				(G, 30.0)
-				(H, 22.3)
-			};
-		\end{axis}
-	\end{tikzpicture}
+	\subsection{Clustering}
 
-	\subsection{Preliminary results}
+	Whereas in \cite{nakai2001substroke} strokes were segmented into substrokes and classified in
+	25 dimensions, our initial feature extraction strategy provides a coarse full--stroke classification
+	in 8 dimensions. By discarding ``pen--up motions,'' we render the system more resilient to erroneous
+	stroke order, at the cost of increasing variability within each cluster.
+
+	\ldots decided to consider the value given by the ``rule of thumb'' $k \approx \sqrt{n / 2}$ proposed in \cite{mardia2005multivariate}
+	as an upper limit to the number of clusters.
+
+	$$ k_{max} = \sqrt{6,396 / 2} \approx 57 $$
+
+	The clusters were generated using the k--means++ algorithm,
+	a variation of Lloyd's algorithm that seeks to improve the selection of the initial centroids. \cite{arthur2007k}
+
+	Based on the information summarized in table \ref{tbl_stroke_analysis}, \ldots
+
+	Total strokes: 78785
+
+	\begin{table}
+		\renewcommand{\arraystretch}{1.3}
+		\caption{Some form of cluster sample}
+		\label{tbl_sample_clusters}
+		\centering
+		\begin{tabular}{c}
+			We could list centroid info and some sample kanji. \\
+			But not \emph{all} the clusters, right? Too many\ldots \\
+		\end{tabular}
+	\end{table}
+
+	%\begin{tikzpicture}[font=\small]
+	%	\begin{axis}[
+	%		ybar,
+	%		bar width=20pt,
+	%		xlabel={Stroke feature classification},
+	%		ylabel={Frequency (\%)},
+	%		ymin=0,
+	%		ymax=40,
+	%		%ytick=\empty,
+	%		xtick=data,
+	%		axis x line=bottom,
+	%		axis y line=left,
+	%		enlarge x limits=0.2,
+	%		symbolic x coords={A, B, C, D, E, F, G, H},
+	%		xticklabel style={anchor=base, yshift=-\baselineskip},
+	%		nodes near coords={\pgfmathprintnumber\pgfplotspointmeta}
+	%	]
+	%		\addplot[fill=white] coordinates {
+	%			(A, 33.2)
+	%			(B, 1.5)
+	%			(C, 0)
+	%			(D, 0)
+	%			(E, 0.3)
+	%			(F, 12.7)
+	%			(G, 30.0)
+	%			(H, 22.3)
+	%		};
+	%	\end{axis}
+	%\end{tikzpicture}
+
+	\section{Preliminary results}
 
@@
 
-	%\section{References}
+	% References
 	\bibliography{./references}

### 2014-08-30 doc/tacs2014/article.tex
Document overview added to introduction, additional references in section II.

@@
 	\section{Introduction}
+	\label{sec:introduction}
 
@@
 	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms; notable successful techniques in
-	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty} \cite{tappert1990state}
+	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty, tappert1990state}
+
+	This paper documents a work in progress on the topic intelligent handwriting recognition of Japanese characters.
+	The remainder of the article is structured as follows:
+	In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for asian script;
+	thereafter in \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
+	An explanation of the proposed solution is given in section \ref{sec:proposed_solution}, and an initial, experimental implementation is described in \ref{sec:experiments}
+	-- the results of which are recorded and examined in section \ref{sec:experiment_results}. Finally, conclusions and future work is presented in sections
+	\ref{sec:conclusions} and \ref{sec:future_work}, respectively.
 
 	\section{Problem description}
+	\label{sec:problem_description}
 
@@
 	and that other characteristics must be taken into account, it becomes apparent that the same designs that
-	yields highly accurate results on the western alphabet will not perform satisfactory when applied to asian character recognition, \cite{tappert1990state}
-	unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}
+	yields highly accurate results on the latin alphabet will not perform satisfactory when applied to asian character recognition \cite{tappert1990state, liu2004online}
+	-- unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}
 
-	In this work, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
+	In continuation, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
 	thereby reducing the complexity of each undertaking. The design scheme also permits replacing classification strategies,
@@
 	\section{Previous work}
+	\label{sec:previous_work}
 
@@
 	\section{Proposed solution}
+	\label{sec:proposed_solution}
 
@@
 	\section{Experiments}
+	\label{sec:experiments}
 
@@
 	\section{Preliminary results}
+	\label{sec:experiment_results}
 
@@
 	\section{Conclusions}
+	\label{sec:conclusions}
 
@@
 	\section{Future work}
+	\label{sec:future_work}
 

### 2014-08-31 doc/tacs2014/article.tex
Added kanji example (yama, ryuu, kane) to illustrate the variance in complexity.
Stroke categories, stroke number histogram, previous work progress

@@
 
-	This paper documents a work in progress on the topic intelligent handwriting recognition of Japanese characters.
+	This paper documents a work in progress on the topic of intelligent handwriting recognition of Japanese characters.
 	The remainder of the article is structured as follows:
@@
 	thereafter in \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
-	An explanation of the proposed solution is given in section \ref{sec:proposed_solution}, and an initial, experimental implementation is described in \ref{sec:experiments}
+	An explanation of our solution approach is given in section \ref{sec:proposed_solution}, and an initial, experimental implementation is described in \ref{sec:experiments}
 	-- the results of which are recorded and examined in section \ref{sec:experiment_results}. Finally, conclusions and future work is presented in sections
 	\ref{sec:conclusions} and \ref{sec:future_work}, respectively.
+
+	\begin{figure}
+		\centering
+		\includegraphics[width=2.75in]{./fig/yama-ryuu-kane.eps}
+		\caption{Sample characters. The kanji ``yama'' (mountain), ``ry\=u'' (dragon), and ``kane'' (bell), written with 3, 10, and 20 strokes, respectively.}
+		\label{fig_kanji_sample}
+	\end{figure}
+
+	\vfill
 
@@
 	everything from the quality and quantity of training data, to resilience toward input
-	translation, rotation, and noise. As the number of candidate categories increases
+	translation, rotation, and noise. As the number of candidate categories increase
 	the size of the search space, however, the task quickly grows monumental.
@@
 
-	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
-	and that other characteristics must be taken into account, it becomes apparent that the same designs that
-	yields highly accurate results on the latin alphabet will not perform satisfactory when applied to asian character recognition \cite{tappert1990state, liu2004online}
-	-- unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}
+	Given that the category search space for Japanese characters is an order of magnitude larger and contains a vastly differing set of
+	characteristics than its western counterparts, the same designs that yield highly accurate results on 
+	western handwriting recognition tasks will not perform satisfactory when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
+	-- unless the solution relies on complex and computationally expensive techniques, such as  ``deep'' neural networks. \cite{ciresan2012multi}
 
 	In continuation, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
-	thereby reducing the complexity of each undertaking. The design scheme also permits replacing classification strategies,
-	and facilitates the parallelization of network training.
+	thereby reducing the complexity of each undertaking. The design scheme also permits replacing the segmentation and classification strategies,
+	and facilitates the parallelization of the fine classification components.
+
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[font=\small]
+			\begin{axis}[
+				ycomb,
+				xlabel={Number of strokes},
+				ylabel={Number of characters},
+			]
+				%\addplot[fill=white] coordinates {
+				\addplot [] coordinates {
+					(1, 6)
+					(2, 32)
+					(3, 64)
+					(4, 115)
+					(5, 151)
+					(6, 199)
+					(7, 318)
+					(8, 434)
+					(9, 473)
+					(10, 544)
+					(11, 581)
+					(12, 581)
+					(13, 532)
+					(14, 435)
+					(15, 434)
+					(16, 369)
+					(17, 299)
+					(18, 207)
+					(19, 175)
+					(20, 135)
+					(21, 106)
+					(22, 69)
+					(23, 49)
+					(24, 37)
+					(25, 20)
+					(26, 12)
+					(27, 8)
+					(28, 6)
+					(29, 3)
+					(30, 2)
+				};
+			\end{axis}
+		\end{tikzpicture}
+		\caption{Distribution of 6,400 kanji by number of stroke. Min = 2, Max = 581. \emph{Data source: KanjiVG.} \cite{kanjivg}}
+		\label{fig_kanji_stroke_hist}
+	\end{figure}
 
@@
 
-	Testing a cite \cite{zhu2014robust}.
+	A vast body of work has been amassed on the topic of Japanese handwriting recognition.
+	Here we summarize some notable publications that influenced our adopted approach.
 
-	\ldots
+	In \cite{joe1989large}, Mori and Joe present ``selective'' and ``integrative'' neural networks that 
+	segment categories into small groups, thereby improving the recognition rate of each network.
 
+	% Took A-H classification from here
 	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
-	hidden Markov models for the purpose of online kanji recognition. By identifying and classifying
-	substrokes, which in turn are employed as search keys in a character dictionary, this approach vastly
-	reduced the memory requirements for both their models and their dictionary.
+	hidden Markov models for the purpose of online kanji recognition. Captured strokes are segmented into
+	substrokes and classified according to directionality (see figure \ref{fig_stroke_categories}),
+	and these characteristics are in turn employed as dictionary search keys.
 
-	In \cite{yang2003accelerating}, clustering, offline recognition, first comparing input to centroid character,
-	therafter search within.
+	After structuring the search space by clustering, Yang et. al. perform two--stepped offline recognition by first
+	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
+	whose centroid most closely matched the input. \cite{yang2003accelerating},
+
+	In \emph{Hybrid pen-input character recognition system based on integration of online-offline recognition},
+	the authors integrate online and offline recognition strategies, leveraging the advantages of each technique.
+	In addition to a discussion of various integration techniques, two feature extraction methods are described: 
+	a gradient--based technique for offline input, and a recursive substroke extractor for online input.
 
@@
 	and discusses the hierarchical structure of kanji.
-
-	``A linear--time elastic matching algorithm for on--line recognition of handwritten Japanese characters'' (Nakagawa)
-	presents the LTM--algorithm, an alternative and attractive way of extracting feature points.
 
@@
 	\label{sec:proposed_solution}
+
+	By structuring the search space into mutually exclusive clusters of similar categories,
+	we are able to construct a corresponding number of fine classifiers that need only distinguish
+	between the categories within its own cluster. The smaller search space directly translates into a
+	significant reduction of model complexity, which in turn implies both a decrease in training time
+	and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
+	between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
+	improved as new training data is made available.
 
@@
 
-	By structuring the search space into mutually exclusive clusters of similar categories,
-	we are able to construct a corresponding number of fine classifiers that need only distinguish
-	between the categories within its own cluster. The smaller search space directly translates into a
-	significant reduction of model complexity, which in turn implies both a decrease in training time
-	and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
-	between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
-	improved as new training data is made available.
+	\begin{figure}
+		\centering
+		\includegraphics[width=1.75in]{./fig/stroke-categories.eps}
+		\caption{A stroke may be classified according to its directionality.
+			Further classes may be used to differentiate between long and short strokes,
+		or to accomodate for ``pen--up'' motions. Here, the strokes of the kanji ``ki'' (tree) are identified as A-G-F-H.}
+		\label{fig_stroke_categories}
+	\end{figure}
 
@@
 		\includegraphics[width=2.75in]{./fig/experimental-implementation.eps}
-		\caption{Experimental implementation. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
+		\caption{Experimental implementation. The input is first analyzed by the coarse classifier, resulting in the G-H-A\ldots feature representation.
 		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
@@
 	Based on the information summarized in table \ref{tbl_stroke_analysis}, \ldots
-
-	Total strokes: 78785
 

### 2014-08-31 doc/tacs2014/article.tex
More or less done with I-III, IVab

@@
 
-	Given that the category search space for Japanese characters is an order of magnitude larger and contains a vastly differing set of
-	characteristics than its western counterparts, the same designs that yield highly accurate results on 
-	western handwriting recognition tasks will not perform satisfactory when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
-	-- unless the solution relies on complex and computationally expensive techniques, such as  ``deep'' neural networks. \cite{ciresan2012multi}
+	Although the characters are vast in number and differ significantly from one another in terms of complexity (see figures \ref{fig_kanji_sample}
+	and \ref{fig_kanji_stroke_hist}), the writing system itself is not arbitrary. Any kanji may be broken down into smaller units, known as graphemes, 
+	and they are commonly ``classified'' by basic, frequently--ocurring components referred to as radicals.
+	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imagined squares. \cite{foerster1994kanji}
 
-	In continuation, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
-	thereby reducing the complexity of each undertaking. The design scheme also permits replacing the segmentation and classification strategies,
-	and facilitates the parallelization of the fine classification components.
+	These properties are often leveraged in kanji recognition systems, but not without penalty: relying on the correct stroke order during online
+	recognition, for instance, severely impacts recognition rates when a user provides ``erroneous'' input -- even though it might still be \emph{visually} correct. \cite{shin2002optimal}
+
+	While certain aspects such as noise reduction and normalization remain similar across systems, the characteristics mentioned above result in
+	recognition systems designed for western input not performing satisfactorily when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
+	-- unless the solution relies on complex techniques such as  ``deep'' neural networks. \cite{ciresan2012multi}
+
+	%Given that the category search space for Japanese characters is an order of magnitude larger and contains a vastly differing set of
+	%characteristics than its western counterparts, the same designs that yield highly accurate results on 
+	%western handwriting recognition tasks do not perform satisfactorily when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
+	%-- unless the solution relies on complex and computationally expensive techniques, such as  ``deep'' neural networks. \cite{ciresan2012multi}
 
@@
 		\end{tikzpicture}
-		\caption{Distribution of 6,400 kanji by number of stroke. Min = 2, Max = 581. \emph{Data source: KanjiVG.} \cite{kanjivg}}
+		\caption{Distribution of 6,400 kanji by stroke count. Min = 2, Max = 581. \emph{Data source: KanjiVG.} \cite{kanjivg}}
 		\label{fig_kanji_stroke_hist}
@@
 
-	% Took A-H classification from here
+	After structuring the search space by clustering, Yang et. al. perform two--stepped offline recognition by first
+	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
+	whose centroid most closely matched the input. \cite{yang2003accelerating}
+
+	In \emph{Hybrid Pen--Input Character Recognition System Based on Integration of Online--Offline Recognition},
+	the authors present a system that leverages the advantages provided by each type of recognition.
+	In addition to a discussion of various integration techniques, two feature extraction methods are described in detail: 
+	a gradient--based technique for offline input, and a recursive substroke extractor for online input.
+
+	% Got A-H classification from here
 	In \cite{nakai2001substroke}, the authors adapt a continuous speech recognition algorithm utilizing
 	hidden Markov models for the purpose of online kanji recognition. Captured strokes are segmented into
-	substrokes and classified according to directionality (see figure \ref{fig_stroke_categories}),
-	and these characteristics are in turn employed as dictionary search keys.
+	substrokes and classified based on directionality (see figure \ref{fig_stroke_categories});
+	the result is thereafter employed as dictionary search keys.
 
-	After structuring the search space by clustering, Yang et. al. perform two--stepped offline recognition by first
-	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
-	whose centroid most closely matched the input. \cite{yang2003accelerating},
+	\emph{Online Handwritten Kanji Recognition Based on Inter--Stroke Grammar} explains the hierarchical structure of kanji,
+	and explores how to leverage this information using stochastic context--free grammars. \cite{ota2007online}
 
-	In \emph{Hybrid pen-input character recognition system based on integration of online-offline recognition},
-	the authors integrate online and offline recognition strategies, leveraging the advantages of each technique.
-	In addition to a discussion of various integration techniques, two feature extraction methods are described: 
-	a gradient--based technique for offline input, and a recursive substroke extractor for online input.
-
-	``Online Handwritten Kanji Recognition Based on Inter-stroke Grammar'' uses the A-H0-9 classification scheme,
-	and discusses the hierarchical structure of kanji.
-
-	Should we mention alternative solutions, such as SVMs? Zinnia (w/ Tomoe) does quite a good job, for instance. Not sure if there
-	are academic evaluations/references, though.
-
-	\section{Proposed solution}
-	\label{sec:proposed_solution}
-
-	By structuring the search space into mutually exclusive clusters of similar categories,
-	we are able to construct a corresponding number of fine classifiers that need only distinguish
-	between the categories within its own cluster. The smaller search space directly translates into a
-	significant reduction of model complexity, which in turn implies both a decrease in training time
-	and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
-	between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
-	improved as new training data is made available.
-
-	\begin{figure}
-		\centering
-		\includegraphics[width=2.75in]{./fig/model-overview.eps}
-		\caption{The model consists of four components: a feature extractor, a clustering strategy,
-			a router (coarse classifier), and a fine--grained classifier.}
-		\label{fig_model_overview}
-	\end{figure}
+	Finally, albeit not directly applied to Japanese handwriting recognition, \emph{Best Practices for Convolutional Neural Networks
+	Applied to Visual Document Analysis} by Simard, et. al. underlines the potential of convolutional neural networks 
+	and provides a variety of techniques and guidelines directly applicable to the development of a fine--grain classifier. \cite{simard2003best}
 
@@
 
+	\section{Proposed solution}
+	\label{sec:proposed_solution}
+
+	Taking into consideration the issues presented in section \ref{sec:problem_description}
+	%the problem posed by the large number of candidates, the characteristics of the kanji writing system,
+	and the many influential works reviewed in section \ref{sec:previous_work}, we attempt to define a general description of a flexble, modular 
+	design scheme that splits the identification task into coarse and fine phases -- thereby reducing the complexity of each undertaking -- and 
+	additionally permits replacing the normalization, segmentation, and classification strategies.%, and facilitates the parallelization of fine classification.
+	The design is applicable to online as well as offline recognition tasks.
+
+	\begin{figure}[b]
+		\centering
+		\includegraphics[width=2.75in]{./fig/model-overview.eps}
+		\caption{The model consists of five components: input normalization methods, a feature extractor,
+			a clustering strategy, a router (coarse classifier), and a fine--grained classifier.}
+		\label{fig_model_overview}
+	\end{figure}
+
+	\subsection{Input normalization}
+
+	Improving the input data, especially by making it more uniform with respect to available training data, has the potential
+	to greatly increase recognition rates. In the case of offline input, techniques include noise--reduction,
+	cropping, and scaling; for online input, strokes could be analyzed and altered on--the--fly to increase consistency.
+	Other possibilities include blurring or otherwise distorting input data in order to generalize it. \cite{razzak2009combining}
+
 	\subsection{Feature extraction}
 
-	The input data is processed by an algorithm, generating a coarse, n--dimensional representation of its principal features.
-	The feature vector is used to select which cluster the input belongs to.
+	The feature extraction algoritm should take either online, offline, or combined input and rapidly generate
+	an n--dimensional vector representation of the provided data. The output should be sufficient for the
+	routing component to reliably distinguish within which candidate subset the fine classifier should search.
 
-	A higher feature vector dimensionality allows for the construction of more finely--tuned clusters, but may well increase
-	the likelihood of ``misrouting,'' resulting in a failed classification.
+	Generally speaking, a higher feature vector dimensionality would allow for the construction of more finely--tuned clusters,
+	but this might well increase the likelihood of misrouting.%, resulting in a failed classification.
 	% Actually, if a character is not found within the specified CANN, it could be passed to a neighboring cluster of similar composition
 
-	The coarse classifier may work on either online or offline input, or potentially a union of them both.
-	Examples of feature extractors include the LTM algorithm, and gradient--based solutions, both outlined in \cite{tanaka1999hybrid}.
+	Examples of feature extractors include recursive substroke segmentation and image gradation, both outlined in \cite{tanaka1999hybrid}.
 
 	\subsection{Category clustering}
+
+	By structuring the search space into mutually exclusive clusters of similar categories,
+	we are able to construct a corresponding number of fine classifiers that need only distinguish
+	between the categories within its own cluster. The smaller search space directly translates into a
+	significant reduction of model complexity, which in turn implies both a decrease in training time
+	and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
+	between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
+	improved as new training data is made available.
 

### 2014-09-01 doc/tacs2014/article.tex
Revamped sections V-VII. Spelling corrections, fitted content to comply with 4-page maximum.

@@
 	\begin{abstract}
-		Quick content summary.
-		Motivation. (From 'Robust': High accuracy has been attained, but speedup/size improvements still important for mobile and desktop.)
+		Handwriting continues to play a significant role in daily life, warranting continued research in the field of intelligent character recognition.
+		Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
+		In this work, we formulate a modular design scheme based on reviews of previous work and the characteristics of the Japanese kanji sinographs.
+		We also describe an ongoing effort to implement and evaluate a basic proof-of-concept handwriting recognition system based on artificial neural networks.
+
 	\end{abstract}
@@
 	\begin{IEEEkeywords}
-		Intelligent character recognition, artificial neural network, handwriting recognition, Japanese writing, \ldots
+		Intelligent character recognition, handwriting recognition, kanji recognition, artificial neural network.
 	\end{IEEEkeywords}
@@
 
-	%Although new technologies aimed at digitalizing every aspect of daily life are introduced and adopted at an ever--increasing pace,
-	%handwriting still remains an integral
-
-	Although a variety of efficient digital input methods have become all but second nature to recent generations, for the vast majority,
+	Although a variety of efficient digital input methods have become all but second nature to recent generations, for the vast majority
 	handwriting remains an integral activity in daily life.
-	The importance to further improve upon the state of the art in handwriting recognition is underlined not only by the continued prevalence of 
+	The importance to further improve upon the state-of-the-art in handwriting recognition is underlined not only by the continued prevalence of 
 	handwriting, but also by the need to digitalize archived material, the significant role of handwriting in the development of fine motor skills,
@@
 
-	As an area of research, handwriting recognition predates even the digital computer. In 1888, Elisha Gray was awarded a patent \cite{gray1888telautograph}
-	for the ``Telautograph,'' which is considered a precursor to the stylus and digitizer.
-	In \cite{dimond1957devices} (1957), T.L. Dimond summarized early character recognition efforts and introduced the Stylator, another input recognition device.
+	As an area of research, handwriting recognition predates even the digital computer. In 1888, Elisha Gray was awarded a patent %\cite{gray1888telautograph}
+	for the ``Telautograph,'' which is considered a precursor to the stylus and digitizer, and in
+	a 1957 publication, T. L. Dimond summarized early character recognition efforts and introduced the Stylator, an early input recognition device. \cite{dimond1957devices}
 
-	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms; notable successful techniques in
+	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms. Noteworthy successful techniques in
 	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty, tappert1990state}
@@
 	The remainder of the article is structured as follows:
-	In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for asian script;
-	thereafter in \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
-	An explanation of our solution approach is given in section \ref{sec:proposed_solution}, and an initial, experimental implementation is described in \ref{sec:experiments}
-	-- the results of which are recorded and examined in section \ref{sec:experiment_results}. Finally, conclusions and future work is presented in sections
-	\ref{sec:conclusions} and \ref{sec:future_work}, respectively.
+	In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for east asian script;
+	in section \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
+
+	An explanation of our solution approach is given in section \ref{sec:proposed_solution}, and an experimental implementation is described in section \ref{sec:experiments}
+	along with some initial observations. Finally, planned future work is presented in section \ref{sec:future_work}, whereafter we conclude by summarizing the
+	contents of this paper in section \ref{sec:summary}.
 
@@
 
-	\vfill
-
 	\section{Problem description}
@@
 	Any form of digital handwriting recognition is a complex undertaking,
-	where the performance of the system is impacted by a multitude of factors -- spanning
+	where the performance of the system is impacted by a multitude of factors---spanning
 	everything from the quality and quantity of training data, to resilience toward input
@@
 	The Japanese writing system consists of the two \emph{kana} syllabaries \emph{hiragana} and \emph{katakana},
-	as well as the sinographs commonly known as \emph{kanji} -- literally ``Han characters'' -- that stem from China.
+	as well as the sinographs commonly known as \emph{kanji}---literally ``Han characters''---that stem from China.
 	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
-	baseline characters taught in elementary-- and secondary--school education. \cite{hadamitzky2012japanese}
+	baseline characters taught in elementary and secondary education. \cite{hadamitzky2012japanese}
 	This set is far from exhaustive, though: the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.
@@
 	and \ref{fig_kanji_stroke_hist}), the writing system itself is not arbitrary. Any kanji may be broken down into smaller units, known as graphemes, 
-	and they are commonly ``classified'' by basic, frequently--ocurring components referred to as radicals.
+	and they are commonly ``classified'' by basic, frequently ocurring components referred to as radicals.
 	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imagined squares. \cite{foerster1994kanji}
@@
 	These properties are often leveraged in kanji recognition systems, but not without penalty: relying on the correct stroke order during online
-	recognition, for instance, severely impacts recognition rates when a user provides ``erroneous'' input -- even though it might still be \emph{visually} correct. \cite{shin2002optimal}
+	recognition, for instance, severely impacts recognition rates when a user provides erroneous input---even though it may still be \emph{visually} correct. \cite{shin2002optimal}
 
 	While certain aspects such as noise reduction and normalization remain similar across systems, the characteristics mentioned above result in
-	recognition systems designed for western input not performing satisfactorily when applied to asian script \cite{jager2003state, tappert1990state, liu2004online}
-	-- unless the solution relies on complex techniques such as  ``deep'' neural networks. \cite{ciresan2012multi}
+	recognition systems designed for western input not performing satisfactorily when applied to east asian script \cite{jager2003state, tappert1990state}%, liu2004online}
+	---unless the solution relies on complex techniques such as  ``deep'' neural networks. \cite{ciresan2012multi}
 
@@
 				ycomb,
-				xlabel={Number of strokes},
-				ylabel={Number of characters},
+				xlabel={Number of Strokes},
+				ylabel={Number of Characters},
 			]
@@
 	A vast body of work has been amassed on the topic of Japanese handwriting recognition.
-	Here we summarize some notable publications that influenced our adopted approach.
+	Here we present a summary of publications dealing with our principal issues of interest,
+	and whose findings motivates our proposal.
+	%Here we summarize some notable publications that influenced our adopted approach.
 
@@
 
-	After structuring the search space by clustering, Yang et. al. perform two--stepped offline recognition by first
+	After structuring the search space by clustering, Yang et al. perform two-stepped offline recognition by first
 	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
@@
 
-	In \emph{Hybrid Pen--Input Character Recognition System Based on Integration of Online--Offline Recognition},
+	In \emph{Hybrid Pen-Input Character Recognition System Based on Integration of Online-Offline Recognition},
 	the authors present a system that leverages the advantages provided by each type of recognition.
 	In addition to a discussion of various integration techniques, two feature extraction methods are described in detail: 
-	a gradient--based technique for offline input, and a recursive substroke extractor for online input.
+	a gradient-based technique for offline input, and a recursive substroke extractor for online input.
 
@@
 	substrokes and classified based on directionality (see figure \ref{fig_stroke_categories});
-	the result is thereafter employed as dictionary search keys.
+	the resulting vector elements are thereafter employed as dictionary search keys.
 
-	\emph{Online Handwritten Kanji Recognition Based on Inter--Stroke Grammar} explains the hierarchical structure of kanji,
-	and explores how to leverage this information using stochastic context--free grammars. \cite{ota2007online}
+	\emph{Online Handwritten Kanji Recognition Based on Inter-Stroke Grammar} explains the hierarchical structure of kanji,
+	and explores how to leverage this information using stochastic context-free grammars. \cite{ota2007online}
 
 	Finally, albeit not directly applied to Japanese handwriting recognition, \emph{Best Practices for Convolutional Neural Networks
-	Applied to Visual Document Analysis} by Simard, et. al. underlines the potential of convolutional neural networks 
-	and provides a variety of techniques and guidelines directly applicable to the development of a fine--grain classifier. \cite{simard2003best}
+	Applied to Visual Document Analysis} by Simard, et al. underlines the potential of convolutional neural networks 
+	and provides a variety of techniques and guidelines directly applicable to the development of a fine-grain classifier. \cite{simard2003best}
 
@@
 			Further classes may be used to differentiate between long and short strokes,
-		or to accomodate for ``pen--up'' motions. Here, the strokes of the kanji ``ki'' (tree) are identified as A-G-F-H.}
+		or to accomodate for ``pen-up'' motions. Here, the strokes of the kanji ``ki'' (tree) are identified as A-G-F-H.}
 		\label{fig_stroke_categories}
@@
 
-	Taking into consideration the issues presented in section \ref{sec:problem_description}
-	%the problem posed by the large number of candidates, the characteristics of the kanji writing system,
-	and the many influential works reviewed in section \ref{sec:previous_work}, we attempt to define a general description of a flexble, modular 
-	design scheme that splits the identification task into coarse and fine phases -- thereby reducing the complexity of each undertaking -- and 
-	additionally permits replacing the normalization, segmentation, and classification strategies.%, and facilitates the parallelization of fine classification.
-	The design is applicable to online as well as offline recognition tasks.
+	%Taking into consideration the issues presented in section \ref{sec:problem_description}
+	Taking the issues presented in section \ref{sec:problem_description} and the many influential works reviewed in section \ref{sec:previous_work}
+	into consideration, an attempt is made to define a general description of a flexble, modular 
+	design scheme that splits the identification task into coarse and fine phases---thereby reducing the complexity of each undertaking---and 
+	additionally permits replacing the normalization, segmentation, and classification strategies. %, and facilitates the parallelization of fine classification.
+	The design scheme is applicable to systems performing online as well as offline recognition tasks.
 
@@
 		\caption{The model consists of five components: input normalization methods, a feature extractor,
-			a clustering strategy, a router (coarse classifier), and a fine--grained classifier.}
+			a clustering strategy, a router (coarse classifier), and a fine-grained classifier.}
 		\label{fig_model_overview}
@@
 	Improving the input data, especially by making it more uniform with respect to available training data, has the potential
-	to greatly increase recognition rates. In the case of offline input, techniques include noise--reduction,
-	cropping, and scaling; for online input, strokes could be analyzed and altered on--the--fly to increase consistency.
+	to greatly increase recognition rates. In the case of offline input, techniques include noise reduction,
+	cropping, and scaling; for online input, strokes may be analyzed and altered on-the-fly to increase consistency.
 	Other possibilities include blurring or otherwise distorting input data in order to generalize it. \cite{razzak2009combining}
@@
 
-	The feature extraction algoritm should take either online, offline, or combined input and rapidly generate
-	an n--dimensional vector representation of the provided data. The output should be sufficient for the
+	The feature extraction algoritm should take online, offline, or combined input and rapidly generate
+	an n-dimensional vector representation of the provided data. The output should be sufficient for the
 	routing component to reliably distinguish within which candidate subset the fine classifier should search.
 
-	Generally speaking, a higher feature vector dimensionality would allow for the construction of more finely--tuned clusters,
+	Generally speaking, a higher feature vector dimensionality would allow for the construction of more finely-tuned clusters,
 	but this might well increase the likelihood of misrouting.%, resulting in a failed classification.
-	% Actually, if a character is not found within the specified CANN, it could be passed to a neighboring cluster of similar composition
 
@@
 
-	By structuring the search space into mutually exclusive clusters of similar categories,
-	we are able to construct a corresponding number of fine classifiers that need only distinguish
-	between the categories within its own cluster. The smaller search space directly translates into a
-	significant reduction of model complexity, which in turn implies both a decrease in training time
-	and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
-	between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
-	improved as new training data is made available.
+	By structuring the search space into clusters of similar categories based on extracted features, we may
+	then construct a corresponding number of fine classifiers that need only concern themselves with distinguishing
+	between the categories within their own clusters. Partitions could either be mutually exclusive or contain some degree of overlap.
 
-	As is proven in \cite{drineas2004clustering}, this is an NP-hard problem even in the case of $k = 2$.
+	K-means clustering is often employed for this type of partitioning task, as is the LGB algorithm. \cite{yang2003accelerating}
+	%It is worth mentioning that optimally allocating $n$ elements in $k$ partitions is an NP-hard problem, even in the case of $k = 2$. \cite{drineas2004clustering}
 
-	Centroid-based clustering
-	"Seeks to minimize the average squared distance between points in the same cluster"
-	goal is to choose k centers so as to minimize $\varphi$, the total squared distance between each point and its closest center.
+	%This translates into significant reductions in model complexity,
+	%which in turn implies both a decrease in training time
+	%and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
+	%between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
+	%improved as new training data is made available.
 
-	\subsection{Feedforward routing network}
+	%Centroid-based clustering
+	%"Seeks to minimize the average squared distance between points in the same cluster"
+	%goal is to choose k centers so as to minimize $\varphi$, the total squared distance between each point and its closest center.
 
-	\subsection{Convolutional character classification network}
+	\subsection{Routing}
 
-	\section{Experiments}
+	Acting upon the vector provided by the feature extractor, the router---or coarse classifier---should indicate
+	within which partition the category corresponding to the input is most likely located. This component could
+	be contrived to indicate not only one but multiple targets in order to dampen the effect of erroneous routing.
+
+	A 2014 publication by Zhu and Nakagawa documents the use of genetic algorithms to programmatically generate robust coarse classifiers. \cite{zhu2014robust}
+
+	\subsection{Fine-grained classification}
+
+	The final and most crucial component of the system is the fine classifier, which is tasked with matching the
+	given input against the candidates within its partition. As mentioned in section \ref{sec:previous_work}, a great
+	variety of techniques exist, including support vector machines, Bayesian networks, hidden Markov models, and artificial neural networks.
+	This step is not necessarily limited to using only one method; provided a reliable means of integration is developed,
+	multiple classifiers could work in unity to provide the best possible classification.
+	%As with the coarse classifier, this component could leverage either of or both online and offline information.
+
+	\section{Experiments \& preliminary results}
 	\label{sec:experiments}
 
-	This will be a short section\ldots
-	Describe the simple online feature extractor and following clustering scheme.
+	Based on the design scheme outlined in the previous section, we are currently in the process of implementing 
+	a basic online kanji recognition system which we aim to evaluate on established testing benchmarks
+	as well as in the form of a mobile application. The diagram in figure \ref{fig_experimental_implementation} 
+	explains how the components interact.
 
@@
 		\caption{Experimental implementation. The input is first analyzed by the coarse classifier, resulting in the G-H-A\ldots feature representation.
-		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
+		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine-grain classification.}
 		\label{fig_experimental_implementation}
@@
 
-	\subsection{Data sources}
+	\subsection{Input normalization}
 
-	KanjiVG \ldots
+	Initially, two alternatives are being explored: an approach in which no input normalization is be applied, and one 
+	in which the effect of rectifying online strokes by altering or discarding points below a certain threshold is evaluated.
 
@@
 
-	Figure of A-H compass. Explanation.
+	With the intent of progressively improving the various facets of the system,
+	our first feature extractor was made as simple as possible: each stroke is directly
+	classified with a letter as illustrated in figure \ref{fig_stroke_categories} based solely
+	on its start and endpoints. Table \ref{tbl_stroke_analysis} contains a summary of the
+	result of classifying the 6,400 elements in the KanjiVG dataset in this manner.
+	We speculate that excluding pen-up motions will result in a more error-resilient system.
 
-	\begin{table}
+	Additional experiments will include distinguishing between long and short strokes,
+	including pen-up motions, and segmenting strokes into substrokes before classification.
+
+	\begin{table}[b]
 		\renewcommand{\arraystretch}{1.3}
@@
 
-	\subsection{Clustering}
+	\subsection{Category clustering}
 
-	Whereas in \cite{nakai2001substroke} strokes were segmented into substrokes and classified in
-	25 dimensions, our initial feature extraction strategy provides a coarse full--stroke classification
-	in 8 dimensions. By discarding ``pen--up motions,'' we render the system more resilient to erroneous
-	stroke order, at the cost of increasing variability within each cluster.
+	Equipped with their respective feature vectors, the 6,400 categories were partitioned into 50
+	mutually exclusive clusters using the K-means++ algorithm. \cite{arthur2007k}
+	Based on the information provided
+	in table \ref{tbl_stroke_analysis}, only the five dimensions A, B, F, G, and H were utilized as sorting parameters.
+	The number of clusters was determined empirically, using Mardia's rule of thumb \mbox{$k \approx \sqrt{n / 2}$} \cite{mardia2005multivariate}
+	as an upper limit.
 
-	\ldots decided to consider the value given by the ``rule of thumb'' $k \approx \sqrt{n / 2}$ proposed in \cite{mardia2005multivariate}
-	as an upper limit to the number of clusters.
+	%\begin{table}
+	%	\renewcommand{\arraystretch}{1.3}
+	%	\caption{Some form of cluster sample}
+	%	\label{tbl_sample_clusters}
+	%	\centering
+	%	\begin{tabular}{c}
+	%		We could list centroid info and some sample kanji. \\
+	%		But not \emph{all} the clusters\ldots TMI. \\
+	%	\end{tabular}
+	%\end{table}
 
-	$$ k_{max} = \sqrt{6,396 / 2} \approx 57 $$
+	\subsection{Routing}
 
-	The clusters were generated using the k--means++ algorithm,
-	a variation of Lloyd's algorithm that seeks to improve the selection of the initial centroids. \cite{arthur2007k}
+	Initially, three simple routing schemes are being applied: a lookup table, a function that
+	identifies the most similar centroid, and a feedforward neural network. One auxiliary goal
+	at this stage---in particular with the ANN---is creating some degree of resilience to errors
+	such as a missing or incorrectly traced strokes.
 
-	Based on the information summarized in table \ref{tbl_stroke_analysis}, \ldots
+	\subsection{Fine-grained classification}
 
-	\begin{table}
-		\renewcommand{\arraystretch}{1.3}
-		\caption{Some form of cluster sample}
-		\label{tbl_sample_clusters}
-		\centering
-		\begin{tabular}{c}
-			We could list centroid info and some sample kanji. \\
-			But not \emph{all} the clusters, right? Too many\ldots \\
-		\end{tabular}
-	\end{table}
+	We are currently designing and evaluating convolutional neural networks to perform final, visual comparisons.
+	Convolutional neural networks are known to provide a measure of resilience against translation and rotation,
+	thus lending themselves well to the task of offline character recognition.
 
-	%\begin{tikzpicture}[font=\small]
-	%	\begin{axis}[
-	%		ybar,
-	%		bar width=20pt,
-	%		xlabel={Stroke feature classification},
-	%		ylabel={Frequency (\%)},
-	%		ymin=0,
-	%		ymax=40,
-	%		%ytick=\empty,
-	%		xtick=data,
-	%		axis x line=bottom,
-	%		axis y line=left,
-	%		enlarge x limits=0.2,
-	%		symbolic x coords={A, B, C, D, E, F, G, H},
-	%		xticklabel style={anchor=base, yshift=-\baselineskip},
-	%		nodes near coords={\pgfmathprintnumber\pgfplotspointmeta}
-	%	]
-	%		\addplot[fill=white] coordinates {
-	%			(A, 33.2)
-	%			(B, 1.5)
-	%			(C, 0)
-	%			(D, 0)
-	%			(E, 0.3)
-	%			(F, 12.7)
-	%			(G, 30.0)
-	%			(H, 22.3)
-	%		};
-	%	\end{axis}
-	%\end{tikzpicture}
+	As previously stated, the comparatively small set of candidates (in current experiments averaging 128 kanji)
+	implies that each cluster model require a lower degree of complexity. Furthermore, our expectation is that---seeing
+	how each partition is likely to contain many similar-looking characters---the networks will be more likely
+	to correctly discern between more minute differences that might have been generalized away in a larger-scale network.
 
-	\section{Preliminary results}
-	\label{sec:experiment_results}
-
-	Not done yet, but here we go.
-
-	\section{Conclusions}
-	\label{sec:conclusions}
-
-	This work is cool, now give complimentary M.Sc. plx?
-	They did it for Donald Knuth\ldots :(
+	Finally, by focusing solely on offline recognition at this stage, we may utilize a significantly larger body of 
+	training data, such as the ETL character database, which contains hundreds of thousands of handwritten kanji samples. \cite{yamamoto1986recognition}
 
@@
 
-	The experimental results documented in this paper are an initial attempt at applying the proposed methodology;
-	numerous variations remain to be explored. With regard to online recognition, the explored feature extraction
+	The experiments documented in this paper are an initial attempt at implementing the outlined design methodology---
+	numerous venues still remain to be explored. With regard to online recognition, for instance, the feature extraction
 	strategy could be enhanced to break strokes into substrokes, diffentiate between long and short strokes, and take
-	pen--up movements into account. This alteration would in turn allow clustering on up to 25 dimensions, rather than the current 8.
+	pen-up movements into account. This alteration would allow for clustering on up to 25 dimensions, rather than the currently used 5.
 
 	By substituting the current coarse classifier with an offline feature extraction strategy, the entire system could
-	be evaluated on offline handwriting recognition datasets, such as\ldots.
+	be applied to exclusively offline handwriting recognition tasks, such as OCR of scanned documents.
 
-	Clustering\ldots
+	At the CANN recognition level, there is ample opportunity both to tweak the network topology and to 
+	to apply a variety of best practices \cite{simard2003best} in order to enhance the final, fine--grain recognition results.
 
-	Finally, at the cluster--specific CANN--level, there is ample opportunity to tweak the network topology as well as
-	to apply a variety of best practices \cite{simard2003best} in order to enhance the final, fine--grain recognition results.
+	By developing and interchanging a series of new, differing components, we ultimately hope to validate the design scheme described in section \ref{sec:proposed_solution}.
+
+	\section{Summary}
+	\label{sec:summary}
+
+	In this paper we provide a general formulation of kanji handwriting recognition systems that encompass a wide range
+	of techniques and use cases, based on an evaluation of the properties and problematics presented by the Japanese writing system,
+	and the review of multiple designs in a corpus of prior work. We also describe our ongoing efforts
+	of applying this design scheme to a basic recognition system, which we aim to continue iterating upon in future works.
 

### 2014-09-01 doc/tacs2014/article.tex
Metadata

@@
 \usepackage[utf8x]{inputenc}
-\usepackage[hidelinks]{hyperref}
+\usepackage[hidelinks,pdftex]{hyperref}
 \usepackage{graphicx}
@@
 
-\title{Some Nice Title Goes Here, Eventually\ldots}
+\hypersetup{
+	pdftitle    = {A Modular Handwritten Kanji Recognition Schema},
+	pdfauthor   = {Lars Fredrik Karlstr\"om and Everardo Guti\'errez L\'opez},
+	pdfsubject  = {Workshop paper on the development of a modular design schema for handwritten kanji recognition.},
+	pdfkeywords = {
+		{Intelligent character recognition}
+		{Handwriting recognition}
+		{Kanji recognition}
+		{Artificial neural network}
+	},
+}
+
+\title{A Modular Handwritten Kanji Recognition Schema}
 
@@
 		Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
-		In this work, we formulate a modular design scheme based on reviews of previous work and the characteristics of the Japanese kanji sinographs.
+		In this work, we formulate a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs.
 		We also describe an ongoing effort to implement and evaluate a basic proof-of-concept handwriting recognition system based on artificial neural networks.
@@
 	into consideration, an attempt is made to define a general description of a flexble, modular 
-	design scheme that splits the identification task into coarse and fine phases---thereby reducing the complexity of each undertaking---and 
+	design schema that splits the identification task into coarse and fine phases---thereby reducing the complexity of each undertaking---and 
 	additionally permits replacing the normalization, segmentation, and classification strategies. %, and facilitates the parallelization of fine classification.
-	The design scheme is applicable to systems performing online as well as offline recognition tasks.
+	The design schema is applicable to systems performing online as well as offline recognition tasks.
 
@@
 
-	Based on the design scheme outlined in the previous section, we are currently in the process of implementing 
+	Based on the design schema outlined in the previous section, we are currently in the process of implementing 
 	a basic online kanji recognition system which we aim to evaluate on established testing benchmarks
@@
 
-	Initially, three simple routing schemes are being applied: a lookup table, a function that
+	Initially, three simple routing strategies are being applied: a lookup table, a function that
 	identifies the most similar centroid, and a feedforward neural network. One auxiliary goal
@@
 
-	By developing and interchanging a series of new, differing components, we ultimately hope to validate the design scheme described in section \ref{sec:proposed_solution}.
+	By developing and interchanging a series of new, differing components, we ultimately hope to validate the design schema described in section \ref{sec:proposed_solution}.
 
@@
 	of techniques and use cases, based on an evaluation of the properties and problematics presented by the Japanese writing system,
-	and the review of multiple designs in a corpus of prior work. We also describe our ongoing efforts
-	of applying this design scheme to a basic recognition system, which we aim to continue iterating upon in future works.
+	and the review of multiple designs in a corpus of prior work. We also describe ongoing efforts
+	of applying this design schema to a basic recognition system, which will be continuously iterating upon in future works.
 

### 2014-09-05 doc/tacs2014/article.tex
Updated figures and various issues

@@
 		Handwriting continues to play a significant role in daily life, warranting continued research in the field of intelligent character recognition.
-		Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
+		%Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
+		East asian scripts, such as Japanese, still remain challenging to process efficiently with high accuracy due to their vast number of symbols.
 		In this work, we formulate a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs.
@@
 	The importance to further improve upon the state-of-the-art in handwriting recognition is underlined not only by the continued prevalence of 
-	handwriting, but also by the need to digitalize archived material, the significant role of handwriting in the development of fine motor skills,
+	handwriting, but also by the need to digitalize archived material, its significant role in the development of fine motor skills,
 	and a variety of other areas of application, such as signature verification. \cite{plamondon2000online}
@@
 	As an area of research, handwriting recognition predates even the digital computer. In 1888, Elisha Gray was awarded a patent %\cite{gray1888telautograph}
-	for the ``Telautograph,'' which is considered a precursor to the stylus and digitizer, and in
+	for the Telautograph, which is considered a precursor to the stylus and digitizer, and in
 	a 1957 publication, T. L. Dimond summarized early character recognition efforts and introduced the Stylator, an early input recognition device. \cite{dimond1957devices}
 
-	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms. Noteworthy successful techniques in
-	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty, tappert1990state}
+	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms, with noteworthy successful techniques
+	currently in widespread use including support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty, tappert1990state}
 
@@
 	The remainder of the article is structured as follows:
-	In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for east asian script;
-	in section \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
+	%In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for east asian script;
+	%in section \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
 
-	An explanation of our solution approach is given in section \ref{sec:proposed_solution}, and an experimental implementation is described in section \ref{sec:experiments}
-	along with some initial observations. Finally, planned future work is presented in section \ref{sec:future_work}, whereafter we conclude by summarizing the
-	contents of this paper in section \ref{sec:summary}.
+	The Japanese writing system and an outline of the primary issues with handwriting recognition for east asian script is presented in section \ref{sec:problem_description}, and
+	in section \ref{sec:previous_work}, some notable advances aimed at solving various aspects of the aforementioned problems are discussed.
+
+	An explanation of the proposed solution approach is given in section \ref{sec:proposed_solution}, and an experimental implementation is described in section \ref{sec:experiments}
+	along with some initial observations. Finally, planned future work is presented in section \ref{sec:future_work}.
+	%whereafter we conclude by summarizing the contents of this paper in section \ref{sec:summary}.
 
@@
 	as well as the sinographs commonly known as \emph{kanji}---literally ``Han characters''---that stem from China.
-	The Japanese Ministry of Education's official ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
+	The Japanese Ministry of Education's \mbox{official} ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
 	baseline characters taught in elementary and secondary education. \cite{hadamitzky2012japanese}
@@
 	and \ref{fig_kanji_stroke_hist}), the writing system itself is not arbitrary. Any kanji may be broken down into smaller units, known as graphemes, 
-	and they are commonly ``classified'' by basic, frequently ocurring components referred to as radicals.
+	and they are commonly ``classified'' by basic, frequently occurring components referred to as radicals.
 	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imagined squares. \cite{foerster1994kanji}
@@
 		\end{tikzpicture}
-		\caption{Distribution of 6,400 kanji by stroke count. Min = 2, Max = 581. \emph{Data source: KanjiVG.} \cite{kanjivg}}
+		\caption{Distribution of 6,400 kanji by stroke count. \emph{Source: KanjiVG.} \cite{kanjivg}}
 		\label{fig_kanji_stroke_hist}
@@
 	A vast body of work has been amassed on the topic of Japanese handwriting recognition.
-	Here we present a summary of publications dealing with our principal issues of interest,
-	and whose findings motivates our proposal.
+	This section provides a summary of publications dealing with our principal issues of interest,
+	and whose findings motivates this proposal.
 	%Here we summarize some notable publications that influenced our adopted approach.
 
-	In \cite{joe1989large}, Mori and Joe present ``selective'' and ``integrative'' neural networks that 
+	In \cite{joe1989large}, Mori and Joe present selective and integrative neural networks that 
 	segment categories into small groups, thereby improving the recognition rate of each network.
@@
 	In addition to a discussion of various integration techniques, two feature extraction methods are described in detail: 
-	a gradient-based technique for offline input, and a recursive substroke extractor for online input.
+	a gradient-based technique for offline input, and a recursive substroke extractor for online input. \cite{tanaka1999hybrid}
 
@@
 
-	Finally, albeit not directly applied to Japanese handwriting recognition, \emph{Best Practices for Convolutional Neural Networks
-	Applied to Visual Document Analysis} by Simard, et al. underlines the potential of convolutional neural networks 
-	and provides a variety of techniques and guidelines directly applicable to the development of a fine-grain classifier. \cite{simard2003best}
+	Finally, \emph{Best Practices for Convolutional Neural Networks Applied to Visual Document Analysis} by Simard, et al. underlines the
+	potential of convolutional neural networks and provides a variety of techniques and guidelines directly applicable to the development of a fine-grain classifier. \cite{simard2003best}
 
@@
 		\centering
-		\includegraphics[width=1.75in]{./fig/stroke-categories.eps}
+		\includegraphics[width=2.75in]{./fig/stroke-categories.eps}
 		\caption{A stroke may be classified according to its directionality.
 			Further classes may be used to differentiate between long and short strokes,
-		or to accomodate for ``pen-up'' motions. Here, the strokes of the kanji ``ki'' (tree) are identified as A-G-F-H.}
+		or to accomodate for pen-up motions. Here, the strokes of the kanji ``ki'' (tree) are identified as A-G-F-H.
+		The dotted lines illustrate the pen-up motions that implicitly connect each successive stroke.}
 		\label{fig_stroke_categories}
@@
 
-	%Taking into consideration the issues presented in section \ref{sec:problem_description}
 	Taking the issues presented in section \ref{sec:problem_description} and the many influential works reviewed in section \ref{sec:previous_work}
-	into consideration, an attempt is made to define a general description of a flexble, modular 
+	into consideration, an attempt is made to define a general description of a flexible, modular 
 	design schema that splits the identification task into coarse and fine phases---thereby reducing the complexity of each undertaking---and 
-	additionally permits replacing the normalization, segmentation, and classification strategies. %, and facilitates the parallelization of fine classification.
+	additionally permits replacing the normalization, extraction, segmentation, and classification strategies.
 	The design schema is applicable to systems performing online as well as offline recognition tasks.
+	Figure \ref{fig_model_overview} provides a high-level overview of the concept.
 
@@
 
-	The feature extraction algoritm should take online, offline, or combined input and rapidly generate
+	The feature extraction algoritm should take online, offline, or combined input, and rapidly generate
 	an n-dimensional vector representation of the provided data. The output should be sufficient for the
@@
 
-	Examples of feature extractors include recursive substroke segmentation and image gradation, both outlined in \cite{tanaka1999hybrid}.
+	Examples of feature extractors include recursive substroke segmentation and image gradation, both described in \cite{tanaka1999hybrid}.
 
@@
 
-	By structuring the search space into clusters of similar categories based on extracted features, we may
-	then construct a corresponding number of fine classifiers that need only concern themselves with distinguishing
-	between the categories within their own clusters. Partitions could either be mutually exclusive or contain some degree of overlap.
+	By structuring the search space into clusters of similar \mbox{categories} based on extracted features,
+	a corresponding number of fine classifiers that need only concern themselves with distinguishing
+	between the symbols within their respective cluster may be constructed.
+	Partitions could either be mutually exclusive or contain some degree of overlap.
 
-	K-means clustering is often employed for this type of partitioning task, as is the LGB algorithm. \cite{yang2003accelerating}
+	K-means clustering is often employed for this type of segmentation task, as is the LGB algorithm. \cite{yang2003accelerating}
 	%It is worth mentioning that optimally allocating $n$ elements in $k$ partitions is an NP-hard problem, even in the case of $k = 2$. \cite{drineas2004clustering}
@@
 
-	The final and most crucial component of the system is the fine classifier, which is tasked with matching the
+	The final component of the system is the fine classifier, which is tasked with matching the
 	given input against the candidates within its partition. As mentioned in section \ref{sec:previous_work}, a great
@@
 
-	Based on the design schema outlined in the previous section, we are currently in the process of implementing 
-	a basic online kanji recognition system which we aim to evaluate on established testing benchmarks
+	%Based on the design schema outlined in the previous section, we are currently in the process of implementing 
+	%a basic online kanji recognition system which we aim to evaluate on established testing benchmarks
+	A basic online kanji recognition system based on the design schema outlined in the previous section is
+	currently being implemented. This system will be evaluated on established testing benchmarks
 	as well as in the form of a mobile application. The diagram in figure \ref{fig_experimental_implementation} 
@@
 	With the intent of progressively improving the various facets of the system,
-	our first feature extractor was made as simple as possible: each stroke is directly
+	the first feature extractor was made as simple as possible: each stroke is directly
 	classified with a letter as illustrated in figure \ref{fig_stroke_categories} based solely
@@
 	We speculate that excluding pen-up motions will result in a more error-resilient system.
-
-	Additional experiments will include distinguishing between long and short strokes,
-	including pen-up motions, and segmenting strokes into substrokes before classification.
 
@@
 			\hline
-			  & \bfseries \% & \small $\sum$ & $\mu$ & $\sigma$ & Highest count \\ 
+			  & \bfseries \% & \small $\sum$ & $\mu$ & $\sigma$ & \footnotesize Highest occurrence \\ 
 			\hline
@@
 	We are currently designing and evaluating convolutional neural networks to perform final, visual comparisons.
-	Convolutional neural networks are known to provide a measure of resilience against translation and rotation,
+	\mbox{Convolutional} neural networks are known to provide a measure of resilience against translation and rotation,
 	thus lending themselves well to the task of offline character recognition.
@@
 	As previously stated, the comparatively small set of candidates (in current experiments averaging 128 kanji)
-	implies that each cluster model require a lower degree of complexity. Furthermore, our expectation is that---seeing
+	implies that each cluster model requires a lower degree of complexity. It may also be expected that---seeing
 	how each partition is likely to contain many similar-looking characters---the networks will be more likely
@@
 
-	Finally, by focusing solely on offline recognition at this stage, we may utilize a significantly larger body of 
-	training data, such as the ETL character database, which contains hundreds of thousands of handwritten kanji samples. \cite{yamamoto1986recognition}
+	Finally, by focusing solely on offline recognition at this stage, a significantly larger body of training data
+	---such as the ETL character database, which contains hundreds of thousands of handwritten kanji samples \cite{yamamoto1986recognition}---may be utilized.
 
-	\section{Future work}
+	\section{Summary \& future work}
 	\label{sec:future_work}
 
-	The experiments documented in this paper are an initial attempt at implementing the outlined design methodology---
-	numerous venues still remain to be explored. With regard to online recognition, for instance, the feature extraction
-	strategy could be enhanced to break strokes into substrokes, diffentiate between long and short strokes, and take
-	pen-up movements into account. This alteration would allow for clustering on up to 25 dimensions, rather than the currently used 5.
+	The experiments documented in this paper are an initial \mbox{attempt} at implementing a kanji handwriting recognition \mbox{system}
+	based on the outlined design methodology---numerous venues still remain to be explored.
 
-	By substituting the current coarse classifier with an offline feature extraction strategy, the entire system could
+	With regard to online recognition, for instance, the feature extraction strategy could be enhanced to break strokes into
+	substrokes, diffentiate between long and short strokes, and take pen-up movements into account.
+	This alteration would allow for clustering on up to 25 dimensions, rather than the currently available 8.
+	Alternatively, by substituting the current coarse classifier with an offline feature extraction strategy, the entire system could
 	be applied to exclusively offline handwriting recognition tasks, such as OCR of scanned documents.
 
+	Additional clustering strategies could be examined, potentially harnessing the hierarchical properties of the symbols.
+	Another venue would be developing a cascading clustering system with multiple coarse lookups, aimed at further
+	reducing the size of the fine-grained classifier's search space.
+
 	At the CANN recognition level, there is ample opportunity both to tweak the network topology and to 
-	to apply a variety of best practices \cite{simard2003best} in order to enhance the final, fine--grain recognition results.
+	to apply a variety of best practices \cite{simard2003best} in order to enhance the final, fine-grain recognition results.
 
@@
 
-	\section{Summary}
-	\label{sec:summary}
-
-	In this paper we provide a general formulation of kanji handwriting recognition systems that encompass a wide range
-	of techniques and use cases, based on an evaluation of the properties and problematics presented by the Japanese writing system,
-	and the review of multiple designs in a corpus of prior work. We also describe ongoing efforts
-	of applying this design schema to a basic recognition system, which will be continuously iterating upon in future works.
+	%\section{Summary}
+	%\label{sec:summary}
+	%
+	%In this paper we provide a general formulation of kanji handwriting recognition systems that encompass a wide range
+	%of techniques and use cases, based on an evaluation of the properties and problematics presented by the Japanese writing system,
+	%and the review of multiple designs in a corpus of prior work. We also describe ongoing efforts
+	%of applying this design schema to a basic recognition system, which will be continuously iterating upon in future works.
 

### 2014-09-05 doc/tacs2014/article.tex
(Probably) final revision

@@
 		%Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
-		East asian scripts, such as Japanese, still remain challenging to process efficiently with high accuracy due to their vast number of symbols.
-		In this work, we formulate a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs.
-		We also describe an ongoing effort to implement and evaluate a basic proof-of-concept handwriting recognition system based on artificial neural networks.
+		East asian scripts, such as Japanese, remain challenging to process efficiently with high accuracy due to their vast number of symbols.
+		In this work, a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs is presented, along with
+		the description of an ongoing effort to implement and evaluate a basic handwriting recognition system that incorporates online feature extraction,
+		category clustering, and artificial neural networks.
 
@@
 	A vast body of work has been amassed on the topic of Japanese handwriting recognition.
-	This section provides a summary of publications dealing with our principal issues of interest,
-	and whose findings motivates this proposal.
+	This section provides a summary of publications dealing with many principal issues of interest,
+	whose findings motivate this proposal.
 	%Here we summarize some notable publications that influenced our adopted approach.
@@
 		or to accomodate for pen-up motions. Here, the strokes of the kanji ``ki'' (tree) are identified as A-G-F-H.
-		The dotted lines illustrate the pen-up motions that implicitly connect each successive stroke.}
+		The dotted lines illustrate the pen-up motions that implicitly connect each successive stroke. Taking these motions into account,
+		the label for the same kanji is A-4-G-3-F-2-H.}
 		\label{fig_stroke_categories}
@@
 
-	%Based on the design schema outlined in the previous section, we are currently in the process of implementing 
-	%a basic online kanji recognition system which we aim to evaluate on established testing benchmarks
-	A basic online kanji recognition system based on the design schema outlined in the previous section is
+	An online kanji recognition system based on the design schema outlined in the previous section is
 	currently being implemented. This system will be evaluated on established testing benchmarks
@@
 	With the intent of progressively improving the various facets of the system,
-	the first feature extractor was made as simple as possible: each stroke is directly
+	the first feature extractor was made as straightforward as possible: each stroke is directly
 	classified with a letter as illustrated in figure \ref{fig_stroke_categories} based solely
@@
 	result of classifying the 6,400 elements in the KanjiVG dataset in this manner.
-	We speculate that excluding pen-up motions will result in a more error-resilient system.
+	%We speculate that excluding pen-up motions will result in a more error-resilient system.
+	Intuitively, excluding pen-up motions should result in a more error-resilient system, due to
+	the correct order of the strokes not being taken into account.
 
@@
 
-	We are currently designing and evaluating convolutional neural networks to perform final, visual comparisons.
+	%We are currently designing and evaluating convolutional neural networks to perform final, visual comparisons.
+	Current efforts are focused on designing and evaluating convolutional neural networks to perform final, visual comparisons.
 	\mbox{Convolutional} neural networks are known to provide a measure of resilience against translation and rotation,
@@
 
-	\section{Summary \& future work}
+	\section{Future work}
 	\label{sec:future_work}
@@
 
-	At the CANN recognition level, there is ample opportunity both to tweak the network topology and to 
-	to apply a variety of best practices \cite{simard2003best} in order to enhance the final, fine-grain recognition results.
-
-	By developing and interchanging a series of new, differing components, we ultimately hope to validate the design schema described in section \ref{sec:proposed_solution}.
-
-	%\section{Summary}
-	%\label{sec:summary}
-	%
-	%In this paper we provide a general formulation of kanji handwriting recognition systems that encompass a wide range
-	%of techniques and use cases, based on an evaluation of the properties and problematics presented by the Japanese writing system,
-	%and the review of multiple designs in a corpus of prior work. We also describe ongoing efforts
-	%of applying this design schema to a basic recognition system, which will be continuously iterating upon in future works.
+	At the fine-grained recognition level, there is ample opportunity both to iterate upon the current convolutional neural network
+	approach---refining the network topology and applying a variety of best practices \cite{simard2003best} in order to enhance the 
+	recognition results---and to pursue other recognition techniques, such as hidden Markov models and support vector machines.
 

### 2014-09-05 doc/tacs2014/article.tex
Decided to remove last 'basic' after all

@@
 		In this work, a modular design schema based on reviews of previous work and the characteristics of the Japanese kanji sinographs is presented, along with
-		the description of an ongoing effort to implement and evaluate a basic handwriting recognition system that incorporates online feature extraction,
+		the description of an ongoing effort to implement and evaluate a handwriting recognition system that incorporates online feature extraction,
 		category clustering, and artificial neural networks.

### 2014-10-05 doc/tacs2014/article.tex
Final revision based on reviewer feedback

@@
 		Handwriting continues to play a significant role in daily life, warranting continued research in the field of intelligent character recognition.
-		%Due to their vast number of symbols, east asian scripts such as Japanese remain challenging to process efficiently with high accuracy.
 		East asian scripts, such as Japanese, remain challenging to process efficiently with high accuracy due to their vast number of symbols.
@@
 		category clustering, and artificial neural networks.
+	\end{abstract}
 
-	\end{abstract}
 	\medskip
@@
 	handwriting, but also by the need to digitalize archived material, its significant role in the development of fine motor skills,
-	and a variety of other areas of application, such as signature verification. \cite{plamondon2000online}
+	and a variety of other areas of application, such as signature verification \cite{plamondon2000online}.
 
@@
 	for the Telautograph, which is considered a precursor to the stylus and digitizer, and in
-	a 1957 publication, T. L. Dimond summarized early character recognition efforts and introduced the Stylator, an early input recognition device. \cite{dimond1957devices}
+	a 1957 publication, T. L. Dimond summarized early character recognition efforts and introduced the Stylator, an early input recognition device \cite{dimond1957devices}.
 
-	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms, with noteworthy successful techniques
-	currently in widespread use including support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty, tappert1990state}
+	The decades of research since has introduced a vast number of recognition methods for writing in any and all forms, with noteworthy successful techniques
+	currently in widespread use including support vector machines, hidden Markov models, and artificial neural networks \cite{fujisawa2008forty, tappert1990state}.
 
@@
 	The Japanese Ministry of Education's \mbox{official} ``regular use'' (j\=oy\=o) kanji list defines a set of 2,136
-	baseline characters taught in elementary and secondary education. \cite{hadamitzky2012japanese}
+	baseline characters taught in elementary and secondary education \cite{hadamitzky2012japanese}.
 	This set is far from exhaustive, though: the Japanese Industrial Standard X 0208 encoding, for instance, contains 6,355 different kanji.
@@
 	and \ref{fig_kanji_stroke_hist}), the writing system itself is not arbitrary. Any kanji may be broken down into smaller units, known as graphemes, 
-	and they are commonly ``classified'' by basic, frequently occurring components referred to as radicals.
-	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imagined squares. \cite{foerster1994kanji}
+	and they are commonly classified by basic, frequently occurring components referred to as radicals.
+	Furthermore, stroke order is dictated by a set of rules. In essence, kanji are written from top to bottom and left to right within imaginary squares \cite{foerster1994kanji}.
 
 	These properties are often leveraged in kanji recognition systems, but not without penalty: relying on the correct stroke order during online
-	recognition, for instance, severely impacts recognition rates when a user provides erroneous input---even though it may still be \emph{visually} correct. \cite{shin2002optimal}
+	recognition, for instance, severely impacts recognition rates when a user provides erroneous input---even though it may still appear to be \emph{visually} correct \cite{shin2002optimal}.
 
-	While certain aspects such as noise reduction and normalization remain similar across systems, the characteristics mentioned above result in
+	While certain aspects such as noise reduction and normalization strategies remain similar across systems, the aforementioned characteristics result in
 	recognition systems designed for western input not performing satisfactorily when applied to east asian script \cite{jager2003state, tappert1990state}%, liu2004online}
-	---unless the solution relies on complex techniques such as  ``deep'' neural networks. \cite{ciresan2012multi}
+	---unless the solution relies on complex techniques such as  ``deep'' neural networks \cite{ciresan2012multi}.
 
@@
 		\end{tikzpicture}
-		\caption{Distribution of 6,400 kanji by stroke count. \emph{Source: KanjiVG.} \cite{kanjivg}}
+		\caption{Distribution of 6,400 kanji by stroke count. \emph{Source: KanjiVG} \cite{kanjivg}.}
 		\label{fig_kanji_stroke_hist}
@@
 	comparing the input character to the centroids of each cluster, and then distinguishing between the members of the cluster
-	whose centroid most closely matched the input. \cite{yang2003accelerating}
+	whose centroid most closely matched the input \cite{yang2003accelerating}.
 
@@
 	In addition to a discussion of various integration techniques, two feature extraction methods are described in detail: 
-	a gradient-based technique for offline input, and a recursive substroke extractor for online input. \cite{tanaka1999hybrid}
+	a gradient-based technique for offline input, and a recursive substroke extractor for online input \cite{tanaka1999hybrid}.
 
@@
 	\emph{Online Handwritten Kanji Recognition Based on Inter-Stroke Grammar} explains the hierarchical structure of kanji,
-	and explores how to leverage this information using stochastic context-free grammars. \cite{ota2007online}
+	and explores how to leverage this information using stochastic context-free grammars \cite{ota2007online}.
 
-	Finally, \emph{Best Practices for Convolutional Neural Networks Applied to Visual Document Analysis} by Simard, et al. underlines the
-	potential of convolutional neural networks and provides a variety of techniques and guidelines directly applicable to the development of a fine-grain classifier. \cite{simard2003best}
+	Finally, \emph{Best Practices for Convolutional Neural Networks Applied to Visual Document Analysis} by Simard, et al. outlines the
+	potential of convolutional neural networks and provides a variety of techniques and guidelines directly applicable to the development of a fine-grain classifier \cite{simard2003best}.
 
@@
 	cropping, and scaling; for online input, strokes may be analyzed and altered on-the-fly to increase consistency.
-	Other possibilities include blurring or otherwise distorting input data in order to generalize it. \cite{razzak2009combining}
+	Other possibilities include blurring or otherwise distorting input data in order to generalize it \cite{razzak2009combining}.
 
@@
 
-	K-means clustering is often employed for this type of segmentation task, as is the LGB algorithm. \cite{yang2003accelerating}
+	K-means clustering is often employed for this type of segmentation task, as is the Linde-Buzo-Gray algorithm.% \cite{yang2003accelerating}.
 	%It is worth mentioning that optimally allocating $n$ elements in $k$ partitions is an NP-hard problem, even in the case of $k = 2$. \cite{drineas2004clustering}
@@
 	Acting upon the vector provided by the feature extractor, the router---or coarse classifier---should indicate
-	within which partition the category corresponding to the input is most likely located. This component could
+	within which partition the category corresponding to the input is most likely located. his component could
 	be contrived to indicate not only one but multiple targets in order to dampen the effect of erroneous routing.
 
-	A 2014 publication by Zhu and Nakagawa documents the use of genetic algorithms to programmatically generate robust coarse classifiers. \cite{zhu2014robust}
+	A 2014 publication by Zhu and Nakagawa documents the use of genetic algorithms to programmatically generate robust coarse classifiers \cite{zhu2014robust}.
 
@@
 
-	\section{Experiments \& preliminary results}
+	%\section{Experiments \& preliminary results}
+	\section{Experimental design \& preliminary results}
 	\label{sec:experiments}
@@
 	currently being implemented. This system will be evaluated on established testing benchmarks
-	as well as in the form of a mobile application. The diagram in figure \ref{fig_experimental_implementation} 
-	explains how the components interact.
+	as well as in the form of a mobile application. The diagram presented in figure \ref{fig_experimental_implementation} 
+	explains how the various components interact.
 
@@
 	the first feature extractor was made as straightforward as possible: each stroke is directly
-	classified with a letter as illustrated in figure \ref{fig_stroke_categories} based solely
-	on its start and endpoints. Table \ref{tbl_stroke_analysis} contains a summary of the
+	classified with a letter, as illustrated in figure \ref{fig_stroke_categories}, based solely
+	on its start and endpoints. Table \ref{tbl_stroke_analysis} presents a statistical overview of the
 	result of classifying the 6,400 elements in the KanjiVG dataset in this manner.
-	%We speculate that excluding pen-up motions will result in a more error-resilient system.
 	Intuitively, excluding pen-up motions should result in a more error-resilient system, due to
-	the correct order of the strokes not being taken into account.
+	the \emph{correct order} of the strokes not being taken into account.
 
@@
 	Equipped with their respective feature vectors, the 6,400 categories were partitioned into 50
-	mutually exclusive clusters using the K-means++ algorithm. \cite{arthur2007k}
+	mutually exclusive clusters using the K-means++ algorithm \cite{arthur2007k}.
 	Based on the information provided
-	in table \ref{tbl_stroke_analysis}, only the five dimensions A, B, F, G, and H were utilized as sorting parameters.
+	in table \ref{tbl_stroke_analysis}, only the five significant dimensions A, B, F, G, and H were utilized as sorting parameters.
 	The number of clusters was determined empirically, using Mardia's rule of thumb \mbox{$k \approx \sqrt{n / 2}$} \cite{mardia2005multivariate}
 	as an upper limit.
-
-	%\begin{table}
-	%	\renewcommand{\arraystretch}{1.3}
-	%	\caption{Some form of cluster sample}
-	%	\label{tbl_sample_clusters}
-	%	\centering
-	%	\begin{tabular}{c}
-	%		We could list centroid info and some sample kanji. \\
-	%		But not \emph{all} the clusters\ldots TMI. \\
-	%	\end{tabular}
-	%\end{table}
 
@@
 	such as a missing or incorrectly traced strokes.
+	A differing aspect at this stage compared to previous works is the vastly decreased number
+	of input features being considered, e.g. 8 versus 256 in \cite{yang2003accelerating}.
 
@@
 
-	%We are currently designing and evaluating convolutional neural networks to perform final, visual comparisons.
 	Current efforts are focused on designing and evaluating convolutional neural networks to perform final, visual comparisons.
 	\mbox{Convolutional} neural networks are known to provide a measure of resilience against translation and rotation,
-	thus lending themselves well to the task of offline character recognition.
+	thus lending themselves well to offline character recognition tasks.
 
-	As previously stated, the comparatively small set of candidates (in current experiments averaging 128 kanji)
-	implies that each cluster model requires a lower degree of complexity. It may also be expected that---seeing
-	how each partition is likely to contain many similar-looking characters---the networks will be more likely
-	to correctly discern between more minute differences that might have been generalized away in a larger-scale network.
+	The comparatively small number of category candidates per cluster (in current experiments averaging 128 kanji)
+	implies that each model will require a lower degree of complexity. Furthermore, as it is probable that each
+	partition will contain many similar-looking categories, it follows that the networks may be more likely to correctly
+	discern between more minute differences that might have been generalized away in larger-scale topologies.
+	These properties may lead to desireable reductions in execution time and storage space requirements,
+	without considerable negative impact on recognition rates.
 
-	Finally, by focusing solely on offline recognition at this stage, a significantly larger body of training data
-	---such as the ETL character database, which contains hundreds of thousands of handwritten kanji samples \cite{yamamoto1986recognition}---may be utilized.
+	%As previously stated, the comparatively small set of category candidates (in current experiments averaging 128 kanji)
+	%implies that each cluster model requires a lower degree of complexity. It may also be expected that---seeing
+	%how each partition is likely to contain many similar-looking characters---the networks will be more likely
+	%to correctly discern between more minute differences that might have been generalized away in a larger-scale network.
+
+	Finally, by focusing solely on offline character recognition at this stage, a significantly larger body of training data---such
+	as the ETL character database, which contains hundreds of thousands of handwritten kanji samples \cite{yamamoto1986recognition}---may be utilized.
 
@@
 
-	The experiments documented in this paper are an initial \mbox{attempt} at implementing a kanji handwriting recognition \mbox{system}
-	based on the outlined design methodology---numerous venues still remain to be explored.
+	The experiments documented in this paper are an initial and ongoing attempt at implementing a kanji handwriting recognition \mbox{system}
+	based on the outlined design methodology; numerous venues still remain to be explored.
 
